\documentclass[12pt, a4paper]{report}
\usepackage{styles}

\begin{document}
  \input{titlepage}
  \blankpage
  \input{titlepage}

  \pagestyle{plain}
  \pagenumbering{roman}
  \nonumchapter{Acknowledgements}
  \nonumchapter{Abstract}
  \input{chapters/abstract.tex}
  \clearpage
  \phantomsection
  \addcontentsline{toc}{chapter}{Table of Contents}
  \tableofcontents
  \clearpage
  \phantomsection
  \addcontentsline{toc}{chapter}{List of Figures}
  \listoffigures
  \clearpage
  \phantomsection
  \addcontentsline{toc}{chapter}{List of Tables}
  \listoftables
  \nonumchapter{List of Abbreviations}
  \input{abbreviations.tex}
  \clearpage
  \pagenumbering{arabic}
  \nonumchapter{Introduction}
  \input{chapters/introduction.tex}

  \chapter{Traineeship report}
    \section{About the company}
    \input{chapters/traineeship_report/about_the_company.tex}
    \clearpage
    \section{Technologies}
    \input{chapters/traineeship_report/technologies.tex}
    \clearpage
      \subsection{ROS}
      \input{chapters/traineeship_report/technologies/ros.tex}
      \clearpage
      \subsection{Gazebo}
      \input{chapters/traineeship_report/technologies/gazebo.tex}
      \subsection{MAVROS}
      \input{chapters/traineeship_report/technologies/mavros.tex}
      \subsection{PX4 Autopilot}
      \input{chapters/traineeship_report/technologies/px4.tex}
      \subsection{Python}
      \input{chapters/traineeship_report/technologies/python.tex}
      \clearpage
      \subsection{Docker}
      \input{chapters/traineeship_report/technologies/docker.tex}
      \subsection{RViz}
      \input{chapters/traineeship_report/technologies/rviz.tex}
    \section{Implementation}
    \input{chapters/traineeship_report/implementation.tex}
      \subsection{Overview}
      \input{chapters/traineeship_report/implementation/overview.tex}
      \clearpage
      \subsection{Architecture}
      \input{chapters/traineeship_report/implementation/architecture.tex}
      \clearpage
      \subsection{Showcase}
      \input{chapters/traineeship_report/implementation/showcase.tex}

  \chapter{Research topic}
  \input{chapters/research_topic.tex}
  \clearpage
    \section{What defines a dynamic indoor environment?}
    \input{chapters/research_topic/dynamic_indoor_environment.tex}
      \subsection{What is the definition of a dynamic environment?}
      \input{chapters/research_topic/environment/dynamic.tex}
      \subsection{What is an indoor environment?}
      \input{chapters/research_topic/environment/indoor.tex}
    \section{How is a UAV able to orientate in its environment?}
    \input{chapters/research_topic/orientation.tex}
      \subsection{How can a UAV observe its environment?}
      \input{chapters/research_topic/orientation/observing.tex}
        \subsubsection{Which sensors can a UAV use for observing its environment?}
        \input{chapters/research_topic/orientation/observing/sensors.tex}
      \subsection{How is a UAV able to execute mapping and localization?}
      \input{chapters/research_topic/orientation/mapping_and_localization.tex}
        \subsubsection{Which SLAM algorithms are eligable for a UAV?}
        \input{chapters/research_topic/orientation/slam_algorithms.tex}
          \paragraph{ORB\hyp{}SLAM2}
          \input{chapters/research_topic/orientation/slam_algorithms/orb_slam2.tex}
          \paragraph{Cartographer}
          \input{chapters/research_topic/orientation/slam_algorithms/cartographer.tex}
          \paragraph{BLAM!}
          \input{chapters/research_topic/orientation/slam_algorithms/blam.tex}
          \paragraph{hdl\_graph\_slam}
          \input{chapters/research_topic/orientation/slam_algorithms/hdl_graph_slam.tex}
          \paragraph{RTAB\hyp{}Map}
          \input{chapters/research_topic/orientation/slam_algorithms/rtab_map.tex}
          \paragraph{Comparison SLAM algorithms}
          \input{chapters/research_topic/orientation/slam_algorithms/comparison.tex}
    \section{How is a path of a UAV to a goal planned?}
    \input{chapters/research_topic/path_planning.tex}
      \subsection{What defines an executable path?}
      \input{chapters/research_topic/path_planning/executable_path.tex}
      \subsection{How is the goal of a UAV defined?}
      \input{chapters/research_topic/path_planning/goal.tex}
      \subsection{Which path planning algorithms are usable?}
      \input{chapters/research_topic/path_planning/algorithms.tex}
        \subsubsection{Dijkstra}
        \input{chapters/research_topic/path_planning/algorithms/dijkstra.tex}
        \subsubsection{Lazy Theta*}
        \input{chapters/research_topic/path_planning/algorithms/lazy_theta_star.tex}
        \subsubsection{A*}
        \input{chapters/research_topic/path_planning/algorithms/a_star.tex}
        \subsubsection{Comparison search algorithms}
        \input{chapters/research_topic/path_planning/algorithms/comparison.tex}
    \section{How can a UAV execute a path?}

    \section{Path execution}
    \input{chapters/research_topic/path_execution.tex}
    \clearpage
    \section{Difficulties}
    \input{chapters/research_topic/difficulties.tex}

  \nonumchapter{Conclusion}
  \nonumchapter{Bibliographical references}
  \printbibliography[heading=none]

  % \renewcommand\thesection{\Alph{section}}  % Alphabetical numbering for subsections
  % \appendix
  % \nonumchapter{Appendices}
  %   \section{Description Appendix A}
  %   \section{Description Appendix B}
  %   \section{Description Appendix C}
\end{document}